---
title: "hCoCena main markdown"
author: "Marie Oestreich, Lisa Holsten, Kilian Dahm, Thomas Ulas"
date: "05 01 2024"
output:
  html_document: default
  pdf_document: default
---

# 0 Overview

This file is the core hCoCena pipeline (required steps only + a few high-value defaults).
Optional exploration and advanced tuning are kept in the satellite script:
[`hcocena_satellite.Rmd`](hcocena_satellite.Rmd).

# 1 Pre-Integration Phase

## 1.1 Load package

```{r}
library(hcocena)
```

## 1.2 Initialize hCoCena object

```{r}
hc <- hc_init()
```

## 1.3 Set paths and output folder

Use this step to define where counts, annotations, reference files, and outputs live.

Key parameters:
- `dir_count_data`, `dir_annotation`: folder paths, or `FALSE` when using in-memory data frames.
- `dir_reference_files`: folder with TF/GMT reference resources.
- `dir_output`: root output folder.

```{r}
# Adapt to your machine:
dir_count_data <- "PATH_TO_FOLDER_THAT_HOLDS_YOUR_GENE_EXPRESSION_TABLES/"
dir_annotation <- "PATH_TO_FOLDER_THAT_HOLDS_YOUR_ANNOTATION_TABLES/"
dir_reference_files <- "PATH_TO_REFERENCE_FILES_FOLDER/"
dir_output <- "PATH_TO_FOLDER_WHERE_HCOCENA_SHOULD_SAVE_ALL_ANALYSIS_OUTPUTS/"

hc <- hc_set_paths(
  hc,
  dir_count_data = dir_count_data,
  dir_annotation = dir_annotation,
  dir_reference_files = dir_reference_files,
  dir_output = dir_output
)

hc <- hc_check_dirs(hc)
hc <- hc_init_save_folder(hc, name = "outputs")
```

## 1.4 Define layers and supplementary databases

This step defines input layers and enrichment resources.

Key parameters:
- `data_sets`: each entry is `c(count_source, annotation_source)`.
- `Tf`, `Go`, `Hallmark`, `Kegg`: filenames in `dir_reference_files`.

Single-dataset default:
- define exactly one layer entry.

If you use multiple datasets:
- add more entries to `data_sets` (one per dataset/layer),
- and keep the order consistent with all layer-wise vectors later
  (`top_var`, `min_corr`, `range_cutoff_length`, `cutoff_vector`).
- Mini example with 2 datasets:
  `data_sets = list(RNA_Seq = c("rna_counts.txt", "rna_annotation.txt"), Array = c("array_counts.txt", "array_annotation.txt"))`

```{r}
hc <- hc_define_layers(
  hc,
  data_sets = list(
    RNA_Seq = c("data_batch_donor.txt", "annotation_seq.txt")
  )
)

hc <- hc_set_supp_files(
  hc,
  Tf = "TFcat.txt",
  Go = "c5.go.bp.v2023.1.Hs.symbols.gmt",
  Hallmark = "h.all.v2023.1.Hs.symbols.gmt",
  Kegg = "c2.cp.kegg.v2023.1.Hs.symbols.gmt"
)
```

## 1.5 Read input data

This imports expression and annotation data for all defined layers.

Key parameters:
- `gene_symbol_col`: gene-symbol column in count table.
- `sample_col`: sample ID column in annotation table.
- `count_has_rn`, `anno_has_rn`: set `TRUE` only if rownames are already stored as first column.

```{r}
hc <- hc_read_data(
  hc,
  sep_counts = "\t",
  sep_anno = "\t",
  gene_symbol_col = "SYMBOL",
  sample_col = "SampleID",
  count_has_rn = FALSE,
  anno_has_rn = FALSE
)

hc <- hc_read_supplementary(hc)
```

## 1.6 Set global defaults

This configures organism, grouping variable, network/cluster minimum sizes, GFC range, and layout.

Key parameters:
- `variable_of_interest`: grouping variable used for GFC summaries.
- `range_GFC`: clipping range for fold changes.
- `layout_algorithm`: default network layout (`"layout_with_stress"`).

```{r}
hc <- hc_set_global_settings(
  hc,
  organism = "human",
  control_keyword = "none",
  variable_of_interest = "time_token",
  min_nodes_number_for_network = 50,
  min_nodes_number_for_cluster = 50,
  range_GFC = 2.0,
  layout_algorithm = "layout_with_stress",
  data_in_log = TRUE
)
```

## 1.7 Set layer-specific defaults

This controls per-layer filtering and correlation search ranges.

Key parameters:
- `top_var`: top-variable genes (`"all"` keeps all genes).
- `min_corr`: lower bound for correlation cutoff scan.
- `range_cutoff_length`: number of tested cutoff points.

Single-dataset default:
- pass one value per parameter.

If you use multiple datasets:
- pass one value per layer in the same order as `data_sets`.
- Mini example with 2 datasets:
  `top_var = c("all", "all"), min_corr = c(0.9, 0.9), range_cutoff_length = c(100, 100), print_distribution_plots = c(FALSE, FALSE)`

```{r}
hc <- hc_set_layer_settings(
  hc,
  top_var = c("all"),
  min_corr = c(0.9),
  range_cutoff_length = c(100),
  print_distribution_plots = c(FALSE)
)
```

For optional QC before network building, see:
- [Satellite: Suggest top variable genes](hcocena_satellite.Rmd#sat-topvar)
- [Satellite: Sample distribution](hcocena_satellite.Rmd#sat-sample-distribution)
- [Satellite: PCA](hcocena_satellite.Rmd#sat-pca)
- [Satellite: Metadata distribution](hcocena_satellite.Rmd#sat-meta-distribution)

## 1.8 Data processing part I

Builds layer-level correlations and intermediate objects up to cutoff selection.

Key parameter:
- `corr_method`: `"pearson"` or `"spearman"`.

```{r}
hc <- hc_run_expression_analysis_1(hc, corr_method = "pearson")
```

## 1.9 Select cutoffs and run part II

Choose final cutoffs, check scale-free behavior, and calculate module-level GFC inputs.

Important:
- `cutoff_vector` order must match layer order in `hc_define_layers()`.

Single-dataset default:
- use one cutoff value.

If you use multiple datasets:
- provide one cutoff per layer, in the same order as `data_sets`.
- Mini example with 2 datasets:
  `cutoff_vector = c(0.974, 0.984)`

Optional cutoff recommendation is in satellite:
- [Satellite: Cutoff tuning](hcocena_satellite.Rmd#sat-cutoff-tuning)

```{r fig.height = 8, fig.width = 15}
hc <- hc_plot_cutoffs(hc, interactive = TRUE)
```

```{r}
hc <- hc_set_cutoff(hc, cutoff_vector = c(0.713))
```

```{r message=FALSE, warning=FALSE}
hc <- hc_plot_deg_dist(hc)
```

```{r fig.width = 13, fig.height = 10, out.width = "100%"}
hc <- hc_run_expression_analysis_2(hc)
```

# 2 Integration Phase

Combine layer-specific networks into one integrated graph.

Key parameters:
- `mode`: `"u"` for union, `"i"` for intersection.
- `multi_edges`: how to resolve duplicated edges across layers.

```{r}
hc <- hc_build_integrated_network(hc, mode = "u", multi_edges = "min")
```

# 3 Post-Integration Core

## 3.1 Detect modules and plot heatmap

Runs community detection and plots the module GFC heatmap.

Key parameters:
- `cluster_algo`: e.g. `"cluster_leiden"`.
- `resolution`: more/less granular modules.
- `partition_type`: Leiden objective.

```{r fig.width = 13, fig.height = 10, out.width = "100%"}
hc <- hc_cluster_calculation(
  hc,
  cluster_algo = "cluster_leiden",
  no_of_iterations = 2,
  resolution = 0.5,
  partition_type = "RBConfigurationVertexPartition",
  max_cluster_count_per_gene = 1
)

hc <- hc_plot_cluster_heatmap(hc)
```

Advanced module tuning and alternatives:
- [Satellite: Export/import clustering](hcocena_satellite.Rmd#sat-export-import)
- [Satellite: Resolution tuning](hcocena_satellite.Rmd#sat-resolution-tuning)
- [Satellite: Module splitting](hcocena_satellite.Rmd#sat-module-splitting)
- [Satellite: Algorithm comparison](hcocena_satellite.Rmd#sat-algo-compare)

## 3.2 Plot network by module

Moved to the satellite workflow:
- [Satellite: Plot network by module](hcocena_satellite.Rmd#sat-network-by-module)

Optional:
- [Satellite: Cytoscape round-trip](hcocena_satellite.Rmd#sat-cytoscape)
- [Satellite: Network by GFC](hcocena_satellite.Rmd#sat-network-gfc)

## 3.3 Functional enrichment

Runs module-level enrichment and stores all result tables in `hc@satellite$enrichments`.

Key parameters:
- `gene_sets`: subset of available databases.
- `top`: top terms per module and database.
- `qval`: significance threshold.

```{r fig.width = 13, fig.height = 10, out.width = "100%", message=FALSE, warning=FALSE}
hc <- hc_functional_enrichment(
  hc,
  gene_sets = c("Hallmark","Kegg","Go"),
  clusters = "all",
  top = 5,
  padj = "BH",
  qval = 0.1
)
```

Optional enrichment extensions:
- [Satellite: Longitudinal enrichment waves](hcocena_satellite.Rmd#sat-longitudinal-enrichment)

## 3.4 TF overrepresentation per module

Moved to the satellite workflow:
- [Satellite: TF overrepresentation per module](hcocena_satellite.Rmd#sat-tf-module)

Optional:
- [Satellite: TF overrepresentation (network-wide)](hcocena_satellite.Rmd#sat-tf-network)

# 4 Optional Analyses in Satellite

For optional steps, use:
- [Satellite: TF overrepresentation per module](hcocena_satellite.Rmd#sat-tf-module)
- [Satellite: Module cell-type annotation](hcocena_satellite.Rmd#sat-celltype-annotation)
- [Satellite: Module-condition significance](hcocena_satellite.Rmd#sat-module-significance)
- [Satellite: AI-assisted module interpretation](hcocena_satellite.Rmd#sat-llm)
- [Satellite: Longitudinal endotype workflow (3 steps)](hcocena_satellite.Rmd#sat-longitudinal)
- [Satellite: Recompute heatmap for meta-cluster x time grouping](hcocena_satellite.Rmd#sat-meta-time-heatmap)

# 5 Save session info

Writes a compact, reproducibility-focused record of settings and inputs.

```{r}
hc <- hc_write_session_info(hc)
```
