---
title: "hcocena satellite markdown"
author: "Marie Oestreich, Lisa Holsten, Kilian Dahm, Thomas Ulas"
date: "05 01 2024"
output: html_document
---

```{r setup, include=FALSE}
library(hcocena)
```

# 0 Satellite Overview

This file contains optional extensions to the core pipeline in `hcocena_main.Rmd`.
Run only the sections relevant to your project.

# 1 Pre-integration QC {#sat-pre-qc}

## Suggest top variable genes {#sat-topvar}

Purpose: suggest a data-driven threshold for top-variable genes.

Key parameter:
- none required; read output and use as guidance for `top_var`.

```{r}
hc <- hc_suggest_topvar(hc)
```

## Sample distribution {#sat-sample-distribution}

Purpose: detect outliers and global sample-shift effects.

Key parameters:
- `plot_type`: `"boxplot"` or `"freqdist"`.
- `log_2`: set `TRUE` only if you need log transform inside plot call.

```{r warning=FALSE}
hc <- hc_plot_sample_distributions(hc, plot_type = "boxplot", log_2 = FALSE, plot = TRUE)
hc <- hc_plot_sample_distributions(hc, plot_type = "freqdist", log_2 = FALSE, plot = TRUE)
```

## PCA {#sat-pca}

Purpose: inspect sample structure before integration.

Key parameter:
- `which`: `"all"`, `"topvar"`, or `"network_genes"`.

```{r warning=FALSE}
hc <- hc_pca(hc, which = "all")
```

## Metadata distribution {#sat-meta-distribution}

Purpose: inspect distribution of metadata across groups.

Key parameters:
- `set`: layer index.
- `group_col`: grouping variable.
- `meta_col`: metadata field to visualize.
- `type`: `"cat"` or `"num"`.

```{r eval=FALSE}
hc <- hc_meta_plot(hc, set = 1, group_col = "time_token", meta_col = "Age", type = "num")
```

# 2 Post-integration module refinement {#sat-module-refinement}

## Export and import clustering {#sat-export-import}

Purpose: reuse or compare clustering solutions.

```{r eval=FALSE}
# Export current module assignment
hc <- hc_export_clusters(hc)

# Import external assignment and replot
gtc <- read.delim("PATH_TO_GENE_TO_CLUSTER_FILE", header = TRUE, sep = "\t", stringsAsFactors = FALSE)
hc <- hc_update_clustering_algorithm(hc, gtc = gtc)
hc <- hc_plot_cluster_heatmap(hc)
```

## Module scores

Purpose: evaluate gene-to-module assignment quality.

```{r eval=FALSE}
hc <- hc_get_module_scores(hc)
```

## Cutoff tuning before final cutoff selection {#sat-cutoff-tuning}

Purpose: recommend stricter/relaxed candidate correlation cutoffs per layer.

Key parameters:
- `apply`: `FALSE` to inspect recommendations first.
- `max_no_networks`: max candidate networks retained per layer.
- `min_node_fraction`: minimum retained node fraction threshold.

```{r eval=FALSE}
hc <- hc_tune_cutoff(
  hc,
  apply = FALSE,
  max_no_networks = 3,
  min_node_fraction = 0.6,
  verbose = TRUE
)

hc@satellite$cutoff_tuning$comparison_with_simple
```

## Resolution tuning {#sat-resolution-tuning}

Purpose: recommend a Leiden resolution before final module detection.

Key parameters:
- `apply`: `FALSE` for recommendation only, `TRUE` to apply directly.

```{r eval=FALSE}
hc <- hc_tune_resolution(hc, apply = FALSE)
hc@satellite$auto_tune$clustering$best
```

## Module splitting {#sat-module-splitting}

Purpose: split broad modules into submodules.

Key parameters:
- `modules`: one or more module labels.
- `resolution`: split strength.
- `resolution_test_only`: `TRUE` to test only.

```{r eval=FALSE, message=TRUE, warning=FALSE}
# Test candidate resolutions
hc <- hc_split_modules(
  hc,
  modules = "M1",
  resolution_grid = c(0.05, 0.1, 0.2, 0.8, 1.0),
  resolution_test_only = TRUE
)

# Apply split
hc <- hc_split_modules(
  hc,
  modules = "M1",
  resolution = 1.0
)

# Remove the last split again
hc <- hc_unsplit_modules(hc, which = "last")

# Remove all split history and restore the original modules
#hc <- hc_unsplit_modules(hc, which = "all")

hc <- hc_plot_cluster_heatmap(hc)
```

## Compare clustering algorithms {#sat-algo-compare}

Purpose: compare Leiden with alternatives before selecting final algorithm.

```{r eval=FALSE}
hc <- hc_algo_alluvial(hc)
hc <- hc_pca_algo_compare(hc)
hc <- hc_update_clustering_algorithm(hc, new_algo = "cluster_infomap")
```

# 3 Network visualization utilities {#sat-network}

## Plot network by module {#sat-network-by-module}

Purpose: inspect the integrated network colored by module assignment.

```{r fig.width=10, fig.height=7}
hc <- hc_plot_integrated_network(hc)
```

## Cytoscape round-trip {#sat-cytoscape}

Purpose: edit layout in Cytoscape and re-import coordinates.

```{r eval=FALSE}
# Docker workflow:
hc <- hc_export_to_local_folder(hc)
# ... edit layout in Cytoscape and save network_layout.csv into output folder ...
hc <- hc_import_layout_from_local_folder(hc)

# Local workflow (Cytoscape open):
# hc <- hc_export_to_cytoscape(hc)
# hc <- hc_import_layout_from_cytoscape(hc)
```

## Network colored by GFC {#sat-network-gfc}

Purpose: show condition-specific GFC on network nodes.

```{r eval=FALSE, fig.width=10, fig.height=7}
hc <- hc_plot_gfc_network(hc)
```

## TF overrepresentation for full network {#sat-tf-network}

Purpose: optional TF enrichment on the full network.

```{r eval=FALSE}
hc <- hc_tf_overrep_network(hc)
```

## Hub and targeted network plots

Purpose: inspect hubs and custom gene/module highlights.

```{r eval=FALSE, warning=FALSE}
hc <- hc_find_hubs(
  hc,
  top = 10,
  save = FALSE,
  tree_layout = FALSE,
  TF_only = "TF",
  plot = TRUE
)

hc <- hc_visualize_gene_expression(
  hc,
  genes = c("STAT6", "MAFG", "ETS2", "RUNX1", "IRF4", "BATF3")
)

hc <- hc_highlight_geneset(
  hc,
  gene_set = c("IRF7", "STAT1", "STAT2", "ETV7"),
  name = "Geneset_IFNg"
)

hc <- hc_colour_single_cluster(hc, cluster = "M1")
```

# 4 Module annotations and interpretation {#sat-module-annotations}

## TF overrepresentation per module {#sat-tf-module}

Purpose: identify candidate TF regulators for selected modules.

```{r eval=FALSE, fig.width = 10, fig.height = 7}
hc <- hc_tf_overrep_module(
  hc,
  clusters = "all",
  topTF = 5,
  topTarget = 5
)
```

## Module cell-type annotation {#sat-celltype-annotation}

Purpose: module-level cell/tissue annotation from Enrichr resources.

Key parameters:
- `databases`: one or more Enrichr databases.
- `mode`: `"coarse"` or `"fine"`.
- `top`: number of top terms per module.
- `qval`: significance threshold.

```{r eval=FALSE}
# Inspect available resources and terms first
hc_list_celltype_databases()

hc_preview_celltype_database(
  database = "Human_Gene_Atlas",
  pattern = "mono|macroph|neutro|lymph|dendritic",
  n = 30
)
```

```{r eval=FALSE, fig.width=13, fig.height=10, out.width="100%", message=TRUE, warning=FALSE}
hc <- hc_celltype_annotation(
  hc,
  databases = c("Human_Gene_Atlas"),
  mode = "coarse",
  top = 3,
  qval = 0.1,
  export_excel = TRUE,
  excel_file = "Module_Celltype_Annotation.xlsx",
  plot_heatmap = TRUE,
  heatmap_file_name = "Heatmap_modules_celltype_annotation.pdf"
)

# Heatmap annotation display control:
# - bar_and_text: stacked bars + dominant label
# - bar: bars only
# - text: dominant label only (space-saving)
hc <- hc_plot_cluster_heatmap(
  hc,
  include_dynamic_enrichment_slots = TRUE,
  celltype_bar_mode = "bar_and_text",
  celltype_bar_top_n = 3,
  celltype_bar_include_other = TRUE,
  celltype_bar_show_dominant = TRUE,
  gfc_legend_side = "right"
)
```

```{r eval=FALSE, fig.width=11, fig.height=6}
# Alternative compact matrix view
ct_mat <- hc_plot_celltype_annotation_matrix(
  hc,
  database = "Human_Gene_Atlas",
  value = "pct",
  top_celltypes = 15,
  include_other = TRUE
)

ct_mat$plot
ct_mat$matrix
```

## Metadata annotation for heatmap

Purpose: add categorical metadata bars to module heatmap columns.

Key parameters:
- `variables`: per-layer metadata column names.
- `variable_label`: label shown in heatmap annotation.

```{r eval=FALSE}
hc <- hc_col_anno_categorical(hc, variables = "cohort", variable_label = "cohort")
hc <- hc_col_anno_categorical(hc, variables = "Intubated", variable_label = "intubated")

# Remove all additional categorical heatmap annotations again
hc@satellite[["column_annos_categorical"]] <- NULL

hc <- hc_plot_cluster_heatmap(hc)
```

## Module-condition significance {#sat-module-significance}

Purpose: test module-level differential behavior between conditions.

Key parameters:
- `condition_col`: usually your variable of interest.
- `run_wilcox`, `run_limma`, `run_lmm`: choose test families.
- `module_significance_method`: select display method in heatmap.

```{r eval=FALSE, fig.width=13, fig.height=10, out.width="100%", message=TRUE, warning=FALSE}
hc <- hc_module_condition_significance(
  hc,
  set = "all",
  condition_col = "condition",
  donor_col = NULL,
  time_col = NULL,
  run_wilcox = TRUE,
  run_limma = TRUE,
  run_lmm = FALSE,
  lmm_include_time = FALSE,
  limma_reference = NULL,
  padj = "BH",
  export_excel = TRUE,
  excel_file = "Module_condition_significance.xlsx"
)

hc <- hc_plot_cluster_heatmap(
  hc,
  include_module_significance = TRUE,
  module_significance_method = "auto",
  module_significance_show_qvalue = FALSE,
  module_significance_annotation_name = "sig"
)
```

## AI-assisted module interpretation {#sat-llm}

Purpose: summarize module biology using Gemini, OpenAI, or vLLM.

Key parameters:
- `module`: one label (e.g. `"M1"`) or `"all"`.
- `biological_context`: study context to guide interpretation.
- `system_instruction`: prompt constraints.
- Provider/model params:
  `llm`, `gemini_model`, `openai_model`, `vllm_model`, `vllm_base_url`.

```{r eval=FALSE}
biological_context <- "maturation of monocytes in preterm infants over the first year of life"

system_instruction <- paste("You are an expert transcriptomics analyst.",  "Task: Infer the overarching biological program from the provided list of co-expressed genes.",  "Use the provided biological context to inform your interpretation and synthesize it into a precise biological description.",  "For the 'contextual_state' field, strictly describe the specific cellular or transcriptional state.",  "Constraint 1: Start your descriptions directly with the relevant nouns or biological terms. Completely omit filler phrases like 'this module' or 'the genes'.",  "Constraint 2: Formulate your answer as a direct biological interpretation based on the supplied genes, without claiming any statistical enrichment tests.",  "Output: Return ONLY a valid JSON object matching the requested schema. Do not output markdown formatting, code blocks, or any conversational text.")

hc <- hc_module_function_llm(
  hc,
  module = "all",
  biological_context = biological_context,
  system_instruction = system_instruction,
  llm = "gemini",
  gemini_model = "gemini-2.5-pro",
  api_key = "YOUR_GEMINI_API_KEY",
  timeout_sec = NULL,
  pause_sec = NULL,
  continue_on_error = TRUE
)

Optional providers:
hc <- hc_module_function_llm(hc, module = "all", llm = "openai",
  openai_model = "gpt-4.1-mini", api_key = "YOUR_OPENAI_API_KEY")

hc <- hc_module_function_vllm(hc, module = "all",
  biological_context = biological_context,
  system_instruction = system_instruction,
  vllm_model = "Qwen/Qwen2.5-VL-32B-Instruct",
  vllm_base_url = "http://bn-hl-compute-8mi210-03:8000/v1",
  api_key = "EMPTY")

plots <- hc_plot_module_function_llm(hc)
print(plots$general_processes)
print(plots$contextual_state)
print(plots$key_regulators)

View(hc@satellite$llm_module_function_summary)
```

# 5 Longitudinal endotype workflow (3 steps) {#sat-longitudinal}

## Step 1: module-wise donor clustering

Purpose: cluster donor trajectories within each module and compute CAP.

Key parameters:
- `donor_col`, `time_col`, `time_levels`: longitudinal design definition.
- `k`: candidate cluster counts per module.
- `rerolls`: stability repetitions.
- `impute_method`, `ntree`: imputation setup.

```{r eval=FALSE, message=TRUE, warning=FALSE}
long_step1 <- hc_longitudinal_step1_module_donor(
  hc,
  donor_col = "PatID",
  time_col = "Timepoint_rough_num",
  time_levels = c("1", "2", "3"),
  k = 2:6,
  rerolls = 1000,
  impute = TRUE,
  impute_method = "rfcont",
  ntree = 10,
  min_cluster_fraction = 0.1,
  score_method = "median",
  seed = 42
)
hc <- long_step1$hc

long_step1$plots$module_means_waves
long_step1$plots$module_cluster_waves
long_step1$plots$module_cluster_heatmap
long_step1$plots$cap_heatmap
```

## Step 2: meta-clustering on CAP

Purpose: derive donor meta-clusters and visualize them in PCA/UMAP space.

Key parameters:
- `dimensions`: number of CAP dimensions used.
- `graph_k`, `resolution`: major controls for meta-cluster granularity.

```{r eval=FALSE, message=TRUE, warning=FALSE}
long_step2 <- hc_longitudinal_step2_meta_clustering(
  hc,
  slot_name = "longitudinal_endotypes",
  dimensions = 4,
  graph_method = "knn",
  knn_method = "annoy",
  graph_k = 7,
  resolution = 0.3,
  leiden_method = "RBConfigurationVertexPartition"
)
hc <- long_step2$hc

long_step2$plots$pca
long_step2$plots$umap
```

## Step 3: module trajectories by meta-cluster

Purpose: plot trajectory waves grouped by inferred meta-clusters.

Key parameters:
- `value_mode`: `"scaled_mean_vst"` (default recommended) or alternative modes.
- `value_range`: y-range for scaled mode (default recommendation: `c(-2, 2)`).
- `free_y`: `FALSE` for comparability across modules.

```{r eval=FALSE, message=TRUE, warning=FALSE}
long_step3 <- hc_longitudinal_step3_meta_module_trajectories(
  hc,
  slot_name = "longitudinal_endotypes",
  facet_ncol = 4,
  free_y = FALSE,
  value_mode = "scaled_mean_vst",
  value_range = c(-2, 2)
)
hc <- long_step3$hc

long_step3$plots$meta_module_waves
```

## Longitudinal enrichment waves by meta-cluster {#sat-longitudinal-enrichment}

Purpose: track enrichment trajectories of top terms across time and meta-clusters.

Key parameters:
- `databases`: one or more enrichment DBs.
- `top`: top terms per module.
- `show_donor_lines`: show faint donor-level lines behind mean trajectories.
- `score_method`: `"ssgsea"` recommended.
- `score_scale`: `"z"` for z-scaled enrichment scores.

```{r eval=FALSE, fig.height=12, fig.width=24, message=TRUE, warning=TRUE}
long_enr <- hc_plot_longitudinal_enrichment_meta_waves(
  hc,
  slot_name = "longitudinal_endotypes",
  databases = c("Kegg", "Hallmark", "Go"),
  top = 3,
  show_donor_lines = TRUE,
  donor_alpha = 0.05,
  donor_linewidth = 0.12,
  score_method = "ssgsea",
  score_scale = "z"
)

for (nm in names(long_enr$plots)) {
  print(long_enr$plots[[nm]])
}
```

## Replot heatmap by meta-cluster x timepoint {#sat-meta-time-heatmap}

Purpose: create a combined grouping (`meta_cluster_time`) and replot GFC heatmap
without re-running network integration/clustering.

Key parameters:
- `donor_col`, `time_col`: annotation fields.
- `group_by` in `hc_change_grouping_parameter`: grouping variable to recompute GFC.
- `col_order`: explicit order of combined groups.

```{r eval=FALSE}
hc <- hc_add_meta_time_grouping(
  hc,
  donor_col = "PatID",
  time_col = "Timepoint_rough",
  grouping_col = "meta_cluster_time"
)

col_order <- hc_get_meta_time_col_order(hc, layer = 1)

hc <- hc_change_grouping_parameter(
  hc,
  group_by = "meta_cluster_time",
  cluster_columns = FALSE,
  col_order = col_order
)
```

# 6 Replot heatmap with alternative grouping

Purpose: quickly test an alternative grouping variable for final heatmap view.

```{r eval=FALSE}
hc <- hc_change_grouping_parameter(hc, group_by = "Timepoint_rough")
```
