---
title: "hcocena: Migrating from legacy hcobject workflows"
package: hcocena
output:
  BiocStyle::html_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{hcocena: Migrating from legacy hcobject workflows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Overview

`hcocena` keeps the historical list-based `hcobject` workflow available while
providing an S4 container for new analyses. The conversion helpers allow
incremental migration without rewriting all downstream code at once.

```{r libraries}
library(hcocena)
```

## Round-trip conversion

The conversion helpers support a lightweight round trip.

```{r roundtrip-conversion}
hc <- hc_init()
legacy <- as_hcobject(hc)
hc_roundtrip <- as_hcocena(legacy)

class(legacy)
sort(names(legacy))[1:8]
methods::is(hc_roundtrip, "HCoCenaExperiment")
slotNames(hc_roundtrip)
```

## Converting an existing workspace

For a previously saved analysis workspace, the migration is a one-line
conversion plus the new object-based API.

```{r workspace-example, eval=FALSE}
# load a workspace that contains a legacy `hcobject`
load("legacy_workspace_with_hcobject.RData")

hc <- as_hcocena(hcobject)

# use object-based API
hc <- hc_set_paths(
  hc,
  dir_count_data = FALSE,
  dir_annotation = FALSE,
  dir_reference_files = tempdir(),
  dir_output = tempdir()
)

# if needed: convert back for legacy custom scripts
hcobject <- as_hcobject(hc)
```

Legacy functions remain available and now emit a migration warning by default.

## Session information

```{r session-info}
sessionInfo()
```
