---
title: "hcocena: S4 Workflow Overview"
package: hcocena
output:
  BiocStyle::html_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{hcocena: S4 Workflow Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Overview

`hcocena` provides a network-centric workflow for single-layer and multi-layer
transcriptomics analyses. The object-oriented API stores assays in
`MultiAssayExperiment` / `SummarizedExperiment` containers via the
`HCoCenaExperiment` class while keeping compatibility with the historical
`hcobject` workflow.

## Installation

```{r install, eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
  install.packages("BiocManager")
}

BiocManager::install("hcocena")
```

## Reproducible toy workflow

```{r libraries}
library(hcocena)
library(MultiAssayExperiment)
library(SummarizedExperiment)
```

The example below uses the toy files shipped with the package.

```{r toy-workflow}
extdir <- normalizePath(system.file("extdata", package = "hcocena"), winslash = "/")
extdir <- paste0(extdir, "/")
outdir <- file.path(tempdir(), "hcocena-vignette-output")
dir.create(outdir, recursive = TRUE, showWarnings = FALSE)

hc <- hc_init()

hc <- hc_set_paths(
  hc,
  dir_count_data = extdir,
  dir_annotation = extdir,
  dir_reference_files = extdir,
  dir_output = outdir
)

hc <- hc_define_layers(
  hc,
  data_sets = list(
    Layer1 = c("toy_layer1_counts.tsv", "toy_layer1_anno.tsv"),
    Layer2 = c("toy_layer2_counts.tsv", "toy_layer2_anno.tsv")
  )
)

hc <- hc_read_data(
  hc,
  sep_counts = "\t",
  sep_anno = "\t",
  gene_symbol_col = "SYMBOL",
  sample_col = "SampleID",
  count_has_rn = FALSE,
  anno_has_rn = FALSE
)

hc <- hc_set_global_settings(
  hc,
  organism = "human",
  control_keyword = "control",
  variable_of_interest = "group",
  data_in_log = TRUE
)
```

The imported assays are available through `MultiAssayExperiment`.

```{r container-inspection}
names(experiments(hc_mae(hc)))
lapply(experiments(hc_mae(hc)), dim)
as.data.frame(SummarizedExperiment::colData(experiments(hc_mae(hc))[[1L]]))
```

Configuration metadata remains attached to the container.

```{r config-inspection}
as.data.frame(methods::slot(hc_config(hc), "global"))
as.data.frame(methods::slot(hc_config(hc), "layer"))[, c("layer_id", "count_source", "annotation_source")]
```

## Next steps

The same object can then be passed through the downstream wrappers such as
`hc_run_expression_analysis_1()`, `hc_set_cutoff()`,
`hc_build_integrated_network()`, and `hc_cluster_calculation()`.

## Session information

```{r session-info}
sessionInfo()
```
